%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Github: https://github.com/harshit2000
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\usepackage{tikz}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }





\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



\begin{center}
    {\Huge \scshape Harshit Gaur} \\ \vspace{1pt}
    New Delhi, India \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-9582705290 ~ \href{mailto:harshit.gaur2720@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{harshit.gaur2720@gmail.com}} ~ 
    \href{https://linkedin.com/in/harshitgaur2/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/harshitgaur2}}  ~
    \href{https://github.com/harshit2000}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/harshit2000}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bharati Vidyapeeth's College Of Engineering}{Aug. 2018 -- Aug. 2022}
      {Bachelor of Technology (Computer Science Engineering)}{New Delhi, India}
      \resumeItem{CGPA : 7}
      
    \resumeSubheading
      {Maharaja Agarsain Public School}{Mar. 2017 -- Apr. 2018}
     {Senior Secondary - 72\%} {New Delhi, India}
     \resumeItem {Secondary - 95\%}
    
 \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{TRAINING AND INTERNSHIPS}
  \resumeSubHeadingListStart

    \resumeSubheading {Tata Consultancy Services \resumeItem  {\href{https://github.com/harshit2000/Summer-Internship-TCS-2020}{\ExternalLink}} } 
      {May 2020 -- August 2020}
      {Summer Project Intern}{New Delhi, Delhi}
      \resumeItemListStart
        \resumeItem{Developed a machine learning model to automate the identification and extraction of different emotions from text based sentences. It helps in analysing the public data and design products accordingly.}
        \resumeItem{Implemented using NLTK, Sklearn, Numpy, Re, Pandas and TextBlob. The problem set was provided by a mentor at TCS. Twitter dataset was used to train the model and two algorithms, LSTM and SGD classifier were  implemented for model creation.}
        \resumeItem{The model was tested with different Tf-idf approaches as well in order to sustain the accuracy of the model. The project was submitted to the mentor for evaluation and passed successfully.}
      \resumeItemListEnd

    \resumeSubheading
      {ByteDance, Ltd.}{December 2019 -- February 2020}
      {Subject Matter Expert}{New Delhi, Delhi}
      \resumeItemListStart
        \resumeItem{Appointed as Subject Matter Expert under the company's Educational Division for the development of new learning platform.}
        \resumeItem{My responsibilities was to create educational video content related to computer science and mathematics subject for the platform and write the documentation for the same.}
        \resumeItem{Handled the quality checks(QC) for each day content and managed content streams for the final deployment.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/harshit2000/SheCare-Breast-Cancer-Detection-Using-Fuzzy-Logic-Expert-System}{Expert System For Breast Cancer Detection \ExternalLink}} $|$ \emph{Python, Tkinter, Fuzzy Logic Toolbox}}{Nov 2020}
          \resumeItemListStart
            \resumeItem{Implemented an Expert System for detection of Breast Cancer based on a knowledge based system.}
            \resumeItem{Used WBCD dataset and implemented the rule base of the system using Decision tree. }
            \resumeItem{Designed a user-friendly interface using Python Tkinter package.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\href{https://harshit2000.github.io/}{Minimalist Portfolio (Flutter for Web) \ExternalLink}} $|$ \emph{Dart, Flutter, Android Studio, JavaScript}}{November 2020}
          \resumeItemListStart
            \resumeItem{Developed a personal portfolio for professional use designed using Flutter UI and Dart. It is minimalist and simple with dark mode enabled. The project is a working demonstration of Flutter for Web}
            \resumeItem{Deployed using Github Pages, the single page app is divided into two sections and designed to give a look of a business card. Flutter for web framework beta was used to create the flutter app as a website.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{\href{https://harshit2000.github.io/MedAssist/app.html}{MedAssist - Your health advisor \ExternalLink}} $|$ \emph{JavaScript, HTML/CSS, API}}{October 2020}
          \resumeItemListStart
            \resumeItem{Designed a simple web application with an integrated chatbot which helps in seeking medical advice and assistance in case of emergencies.}
            \resumeItem{Functionalities added to book an appointment with a doctor(Practo), prescribes basic medicines for common ailments like stomach ache, headache, etc., COVID19 assistance and ambulance services}
            \resumeItem{Implemented using Snatchbot NLP API with HTML frontend and Javascript used for authentication and connection routes.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Python, C, JavaScript, MySQL} \\
     \textbf{Technologies/Frameworks}{: Linux, Git, Django, MongoDB } \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{BVPIEEE - IEEE Section Delhi}{May 2019 - December 2021}{Vice President IAS Chapter, Head of Corporate Affairs and Business Development}{\href{https://www.linkedin.com/company/bvp-ieee/mycompany/}\ExternalLink}
            \resumeItemListStart
                \resumeItem{Managed a team for managing the societies' activities regarding workshops, hackathons, events and recruitment.}
                \resumeItem{Led chapter of 10 members to work towards goals that improve and promote community service, academics, and unity.}
            \resumeItemListEnd
        \resumeSubheading{4 Star Rated Programmer at CodeChef}{Present}{C++}
        {\href{https://www.codechef.com/users/harshgaur27}\ExternalLink}
    \resumeSubHeadingListEnd


\end{document}

